Stack Safety as a Security Property

### 2020-07-02 main.tex
Notes

\bcp{
Comments on the example:
\begin{itemize}
\item We can simplify a bit by renaming $f$ to $\mathit{main}$ and
relocating its stack to location 1000.  And maybe move its instructions to
start at 0.  (We can comment that on a real RISC-V this is where interrupt
handlers go, but POPL readers will not care too much.)  We should streamline
the example as much as possible.
\item Do we need the ``...''s in $f$?
%
\item We should also emphasize, again, that there is no heap (if there were,
we might put it above the stack or between the instructions and the stack).
%
\item We will also need to be careful about fonts ($f$ vs {\texttt f}),
capitalization of register names (sp vs SP), etc. Maybe typeset instructions
in small caps?  Maybe typeset everything that is part of a concrete machine
in small caps??
%
\item The colors are helpful in making the big page of instruction traces easier
on the eye; maybe they would be even more helpful if
corresponding colors appeared elsewhere in the example (on the instructions
themselves, e.g.).  But we need to be careful to keep it readable -- maybe
they should be background colors, like you've done, rather than text colors.
\item The first column of numbers is redundant with the second column (PC).
Suggest deleting the first.
\item Asking readers to wade through all this is asking quite a bit!  We
need to make sure we are going to get sufficient value out of the example
later (I think we can, but we should really convince ourselves) to make it
worthwhile.
\item Use ``='' instead of ``:'' in the ``summaries'' below the pictures.
And put a bit more space between the components.
\item Create a new column that just literally pronounces each instruction in
English, so people don't have to read RISC-V opcodes.
\item As discussed, we should move this to before section 2, we should
extend it with a bit more at the end so we can talk about the lazy policy
with the same example, we should add
in some bad variants, and we should consider discussing the attacker model
here (we need to discuss it someplace in any case!)
\end{itemize}
}

@@

  \bcp{Illustrate the definition by using it to discuss a range of ``stack
    unsafety'' examples from the literature. }

@@

>>>>

\bcp{
Comments on the example:
\begin{itemize}
\item We can simplify a bit by renaming $f$ to $\mathit{main}$ and
relocating its stack to location 1000.  And maybe move its instructions to
start at 0.  (We can comment that on a real RISC-V this is where interrupt
handlers go, but POPL readers will not care too much.)  We should streamline
the example as much as possible.
\item Do we need the ``...''s in $f$?
%
\item We should also emphasize, again, that there is no heap (if there were,
we might put it above the stack or between the instructions and the stack).
%
\item We will also need to be careful about fonts ($f$ vs {\texttt f}),
capitalization of register names (sp vs SP), etc. Maybe typeset instructions
in small caps?  Maybe typeset everything that is part of a concrete machine
in small caps??
%
\item The colors are helpful in making the big page of instruction traces easier
on the eye; maybe they would be even more helpful if
corresponding colors appeared elsewhere in the example (on the instructions
themselves, e.g.).  But we need to be careful to keep it readable -- maybe
they should be background colors, like you've done, rather than text colors.
\item The first column of numbers is redundant with the second column (PC).
Suggest deleting the first.
\item Asking readers to wade through all this is asking quite a bit!  We
need to make sure we are going to get sufficient value out of the example
later (I think we can, but we should really convince ourselves) to make it
worthwhile.
\item Use ``='' instead of ``:'' in the ``summaries'' below the pictures.
And put a bit more space between the components.
\item Create a new column that just literally pronounces each instruction in
English, so people don't have to read RISC-V opcodes.
\item As discussed, we should move this to before section 2, we should
extend it with a bit more at the end so we can talk about the lazy policy
with the same example, we should add
in some bad variants (doing it here replaces the ``Examples'' from the
Discussion section), and we should consider discussing the attacker model 
here (we need to discuss it someplace in any case!)
\end{itemize}
}

@@

\bcp{Belongs with the running example:}
  \bcp{Illustrate the definition by using it to discuss a range of ``stack
    unsafety'' examples from the literature. }

@@

\bcp{And this and the next belong in Future Work...}
